Hand picking similar behaving group of customers to check clustering results

### 2021-08-18 supplementary/algorithm2/real-data/algo2-elec100-onegran.Rmd
cleaning folders

##----harmony-all
elec_harmony_all <- read_rds("../data/algo2-rawdata-wpd.rds")

@@

elec_sig_split <- elec_harmony_all %>%
  mutate(facet_variable = case_when(
    facet_variable == "hour_day" ~ "hod" ,
    facet_variable == "day_month" ~ "dom" ,
    facet_variable == "day_week" ~ "dow" ,
    facet_variable == "week_month" ~ "wom" ,
    facet_variable == "wknd_wday" ~ "wdwnd"
  )) %>% 
  mutate(x_variable = case_when(
    x_variable == "hour_day" ~ "hod" ,
    x_variable == "day_month" ~ "dom" ,
    x_variable == "day_week" ~ "dow" ,
    x_variable == "week_month" ~ "wom" ,
    x_variable == "wknd_wday" ~ "wdwnd"
  )) %>% 
  bind_cols(select_split = select_split) %>% 
  mutate(significant = case_when(
    select_split == "***" ~ "highest",
    select_split == "**" ~ "high",
    select_split == "*" ~ "medium",
    select_split == "" ~ "low"
  )) %>%mutate(comb = paste(facet_variable, x_variable, sep = "-"))

@@

ggpairs_nocolor <- ggscatmat(data_pcp_ge2, columns=3:7) +
  scale_colour_brewer(palette="Set2") + theme(legend.position = "bottom")

ggpairs_color <- ggscatmat(data_pcp_ge2, columns=3:7, color = "group") +
  scale_colour_brewer(palette="Set2") + theme(legend.position = "bottom")

@@

sm_hod_dow <- elec_scaled %>% 
gravitas::create_gran("hour_day") %>% 
  gravitas::create_gran("day_week")

sm_hod_list <- sm_hod_dow %>% 
  as_tibble() %>% 
  arrange(group, day_week, hour_day) %>% 
  mutate(category = paste(hour_day, day_week, sep = "-")) %>% 
   select(group, category, general_supply_kwh) %>% 
  pivot_wider(names_from = category,
              values_from = general_supply_kwh)

elec %>% as_tibble() %>% group_by(group) %>% summarise(n = length(unique(customer_id)))

quantile_prob_val = c(0.25, 0.5, 0.75)

p1 <- sm_hod_dow %>% 
  filter(group==1) %>% 
  gravitas::prob_plot(
     "day_week",
     "hour_day",
  response = "general_supply_kwh",
  plot_type = "quantile", nrow=1) +
  scale_y_log10() +
    ggtitle("Group 1") + theme_bw()  +
  theme(legend.position = "none",
        strip.text = element_text(size = 10, margin = margin())) + 
  theme(panel.spacing =unit(0, "lines"))+ ylab("")+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, size = 5))

p2 <- sm_hod_dow %>% 
  filter(group==2 ) %>% 
  gravitas::prob_plot(  "day_week",
     "hour_day",
  response = "general_supply_kwh",
  plot_type = "quantile", nrow=1) +
  scale_y_log10()+
    ggtitle("Group 2")+ theme_bw()  +
  theme(legend.position = "none",
        strip.text = element_text(size = 10, margin = margin())) + 
  theme(panel.spacing =unit(0, "lines"))+ ylab("")+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, size = 5))

p3 <- sm_hod_dow %>% 
  filter(group==3) %>% 
  gravitas::prob_plot(  "day_week",
     "hour_day",
  response = "general_supply_kwh",
  plot_type = "quantile", nrow=1) +
  scale_y_log10() +
    ggtitle("Group 3" )+ theme_bw()  +
  theme(legend.position = "none",
        strip.text = element_text(size = 10, margin = margin())) + 
  theme(panel.spacing =unit(0, "lines"))+ ylab("")+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, size = 5))

p4 <- sm_hod_dow %>% 
  filter(group==4) %>% 
  gravitas::prob_plot("day_week",
     "hour_day",
  response = "general_supply_kwh",
  plot_type = "quantile", nrow=1) +
  scale_y_log10() +
    ggtitle("Group 4")+ theme_bw()  +
  theme(legend.position = "none",
        strip.text = element_text(size = 10, margin = margin())) + 
  theme(panel.spacing =unit(0, "lines"))+ ylab("")+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, size = 5))

p5 <- sm_hod_dow %>% 
  filter(group==5) %>% 
  gravitas::prob_plot("day_week",
     "hour_day",
  response = "general_supply_kwh",
  plot_type = "quantile", nrow=1) +
  scale_y_log10() +
    ggtitle("Group 5")+ theme_bw()  +
  theme(legend.position = "none",
        strip.text = element_text(size = 10, margin = margin())) + 
  theme(panel.spacing =unit(0, "lines"))+ ylab("")+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, size = 5))

p6 <- sm_hod_dow %>% 
  filter(group==6) %>% 
  gravitas::prob_plot("day_week",
     "hour_day",
  response = "general_supply_kwh",
  plot_type = "quantile", nrow=1) +
  scale_y_log10() +
    ggtitle("Group 6")+ theme_bw()  +
  theme(legend.position = "none",
        strip.text = element_text(size = 10, margin = margin())) + 
  theme(panel.spacing =unit(0, "lines"))+ ylab("")+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, size = 5))

p7 <- sm_hod_dow %>% 
  filter(group==7) %>% 
  gravitas::prob_plot("day_week",
     "hour_day",
  response = "general_supply_kwh",
  plot_type = "quantile", nrow=1) +
  scale_y_log10() +
    ggtitle("Group 7")+ theme_bw()  +
  theme(legend.position = "none",
        strip.text = element_text(size = 10, margin = margin())) + 
  theme(panel.spacing =unit(0, "lines"))+ ylab("")+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, size = 5))

p8 <- sm_hod_dow %>% 
  filter(group==8) %>% 
  gravitas::prob_plot("day_week",
     "hour_day",
  response = "general_supply_kwh",
  plot_type = "quantile", nrow=1) +
  scale_y_log10() +
    ggtitle("Group 8")+ theme_bw()  +
  theme(legend.position = "none",
        strip.text = element_text(size = 10, margin = margin())) + 
  theme(panel.spacing =unit(0, "lines")) + ylab("")+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, size = 5))

```

_Regular scale_

```{r}
(p1 + p2)/ (p3 + p4)
(p5 + p6)/(p7 +p8)
```

_Same scale_

```{r}
(p1 +ylim(0,3) + p2 +ylim(0,3))/ (p3+ylim(0,3) + p4+ylim(0,3))
(p5 +ylim(0,3) + p6 +ylim(0,3))/ (p7+ylim(0,3) + p8+ylim(0,3))
```
# PCA based clustering

```{r}
pc <- prcomp(data_pcp[c(-1,-2)], center = F, scale = F)
summary(pc)
# First two principal componentsafc
comp <- data.frame(pc$x[,1:2])

#plot(comp, pch=16, col=rgb(0,0,0,0.5))

hc = stats::hclust(dist(comp))
data_pcp_all <- data_pcp %>% bind_cols(comp)

library(RColorBrewer)
library(scales)
data_pcp_all %>% ggplot(aes(x=PC1, y = PC2)) + geom_point(aes(color = group)) +
  scale_color_brewer(palette = "Dark2") + theme_bw() + theme(legend.position = "bottom")

data_pcp_all %>%
  pivot_longer(-c(1, 2,8, 9), names_to = "variables", values_to = "wpd") %>% 
  ggplot(aes(x=wpd, y = PC1)) + geom_point(aes(color = group)) +
  scale_color_brewer(palette = "Dark2") + theme_bw() +
  facet_wrap(~variables, nrow = 1) + theme(legend.position = "bottom")
```

One dimensional scale since PC1 explains almost all variation?

>>>>

##----harmony-all
elec_harmony_all <- read_rds("../data/elec_harmony-100-nogap-onegran.rds")

@@

elec_sig_split <- elec_harmony_all %>%
  mutate(facet_variable = case_when(
    facet_variable == "hour_day" ~ "hod" ,
    facet_variable == "day_month" ~ "dom" ,
    facet_variable == "day_week" ~ "dow" ,
    facet_variable == "week_month" ~ "wom" ,
    facet_variable == "wknd_wday" ~ "wdwnd"
  )) %>% 
  mutate(x_variable = case_when(
    x_variable == "hour_day" ~ "hod" ,
    x_variable == "day_month" ~ "dom" ,
    x_variable == "day_week" ~ "dow" ,
    x_variable == "week_month" ~ "wom" ,
    x_variable == "wknd_wday" ~ "wdwnd"
  )) %>% 
  bind_cols(select_split = select_split) %>% 
  mutate(significant = case_when(
    select_split == "***" ~ "highest",
    select_split == "**" ~ "high",
    select_split == "*" ~ "medium",
    select_split == "" ~ "low"
  )) %>%mutate(comb = x_variable)

@@

ggpairs_nocolor <- ggscatmat(data_pcp_ge2, columns=3:6) +
  scale_colour_brewer(palette="Set2") + theme(legend.position = "bottom")

ggpairs_color <- ggscatmat(data_pcp_ge2, columns=3:6, color = "group") +
  scale_colour_brewer(palette="Set2") + theme(legend.position = "bottom")

@@

sm_hod_dow <- elec_scaled %>% 
gravitas::create_gran("hour_day")

sm_hod_list <- sm_hod_dow %>% 
  as_tibble() %>% 
  arrange(group, hour_day) %>% 
  mutate(category = hour_day) %>% 
   select(group, category, general_supply_kwh) %>% 
  pivot_wider(names_from = category,
              values_from = general_supply_kwh)

elec %>% as_tibble() %>% group_by(group) %>% summarise(n = length(unique(customer_id)))
```

```{r}
quantile_prob_val = c(0.25, 0.5, 0.75)

sm_hod <- gravitas::create_gran(sm, "hour_day") %>% 
  mutate(customer_id = as.integer(customer_id))

sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(customer_id, hour_day, general_supply_kwh) %>% 
  pivot_wider(names_from = hour_day,
              values_from = general_supply_kwh)

groups_ref <- groups %>% as_tibble %>% 
              mutate(customer_serial_id = sm_hod_list$customer_id) %>% 
             rename ("group" = "value")

sm_hod_list_cat <-  sm_hod_list %>% left_join(groups_ref, by = c("customer_id" = "customer_serial_id")) %>% select(group, everything())

ncol_sm <- seq_len(ncol(sm_hod_list_cat[-c(1, 2)]))
nrow_sm <- unique(sm_hod_list_cat$group)

sm_hod_quantiles_cat <- map(nrow_sm, function(x){
  map(ncol_sm, function(y){
   cell <- sm_hod_list_cat%>% 
     dplyr::filter(group == x) %>% 
     select(-c(1, 2)) %>% 
     extract(y) %>% 
     unlist()
   quantile(cell, prob = quantile_prob_val)
})  %>% bind_rows(.id = "categories_serial_id")
}) %>% bind_rows(.id = "group_id") %>% 
  mutate(group_id = as.integer(group_id),
         categories_serial_id = as.integer(categories_serial_id))

categories_ref_cat <- names(sm_hod_list_cat)[-c(1, 2)] %>% as_tibble() %>% 
  mutate(categories_serial_id = row_number())

data_heatmap <- sm_hod_quantiles_cat %>% 
  pivot_longer(-c(1, 2), names_to = "quantile_prob", values_to = "quantile_val") %>% 
  left_join(categories_ref_cat) %>% 
  rename("category" = "value") %>% 
  select(-categories_serial_id) %>% 
  mutate(category = as.numeric(category))
```

```{r cluster-characterization}
data_heatmap %>% 
  pivot_wider( names_from = quantile_prob, 
               values_from = quantile_val) %>% 
  ggplot(aes(x = category)) +  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`)) +
  facet_wrap(~group_id, ncol = 1, scales = "free_y", labeller = "label_both") +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))

### 2021-08-18 supplementary/algorithm2/real-data/algo2-elec100.Rmd
cleaning folders

```{r}
(p1 +ylim(0,3) + p2 +ylim(0,3))/ (p3+ylim(0,3) + p4+ylim(0,3))
(p5 +ylim(0,3) + p6 +ylim(0,3))/ (p7+ylim(0,3) + p8+ylim(0,3))
```
# PCA based clustering

@@

>>>>

```{r}
(p1 +ylim(0,3) + p2 +ylim(0,3))/ (p3+ylim(0,3) + p4+ylim(0,3))
(p5 +ylim(0,3) + p6 +ylim(0,3))/ (p7+ylim(0,3) + p8+ylim(0,3))
```

# PCA based clustering

@@

#Group2: n=24
```{r}
group2_data <- sm_hod_dow %>% 
  as_tibble() %>% 
  filter(group==2) %>% 
  group_by(day_week, hour_day, customer_id) %>% 
  summarise(median_kwh = median(general_supply_kwh))

group2_data%>% 
  ungroup() %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
  ggplot(aes(x = as.integer(hour_day), y = median_kwh)) +
  geom_line(size = 0.5) +
  facet_grid(customer_id~day_week, scales = "free_y") + theme_minimal()+ theme(strip.text.y = element_text(size = 5))
```

#Group4: n=24
```{r}
group2_data <- sm_hod_dow %>% 
  as_tibble() %>% 
  filter(group==4) %>% 
  group_by(day_week, hour_day, customer_id) %>% 
  summarise(median_kwh = median(general_supply_kwh))

group2_data%>% 
  ungroup() %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
  ggplot(aes(x = as.integer(hour_day), y = median_kwh)) +
  geom_line(size = 0.5) +
  facet_grid(customer_id~day_week, scales = "free_y") + theme_minimal()+ theme(strip.text.y = element_text(size = 5))
```

#Group5: n=18
```{r}
group2_data <- sm_hod_dow %>% 
  as_tibble() %>% 
  filter(group==5) %>% 
  group_by(day_week, hour_day, customer_id) %>% 
  summarise(median_kwh = median(general_supply_kwh))

group2_data%>% 
  ungroup() %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
  ggplot(aes(x = as.integer(hour_day), y = median_kwh)) +
  geom_line(size = 0.5) +
  facet_grid(customer_id~day_week, scales = "free_y") + theme_minimal()+ theme(strip.text.y = element_text(size = 5))
```

#Group6: n=23
```{r}
group2_data <- sm_hod_dow %>% 
  as_tibble() %>% 
  filter(group==6) %>% 
  group_by(day_week, hour_day, customer_id) %>% 
  summarise(median_kwh = median(general_supply_kwh))

group2_data%>% 
  ungroup() %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
  ggplot(aes(x = as.integer(hour_day), y = median_kwh)) +
  geom_line(size = 0.5) +
  facet_grid(customer_id~day_week, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))
```

### 2021-08-18 supplementary/algorithm2/real-data/algo2-elec8.Rmd
cleaning folders

---
title: "Algorithm using wpd values for clustering 8 households"
author: "Sayani Gupta"
date: "13/07/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

hc = stats::hclust(dist(data_clust[-1]),method="complete")
#plot(hc)

library(fpc)
koptimal = fpc::nselectboot(dist(data_clust[-1]),
                        B = 50,
                        method = "complete",
                        clustermethod = disthclustCBI, 
                        classification = "averagedist",
                        krange = 2:8)

koptimal = koptimal$kopt

@@

@@

data = data_clust %>% 
left_join(groups)%>% 
             rename ("group" = "value") %>% 
             ungroup() %>% 
             select(group, everything(), -id) %>% 
             pivot_longer(-1, names_to = "comb", values_to = "wpd")

data_order <- data %>% 
  group_by(comb) %>% 
  summarise(m = mean(wpd)) %>% 
  arrange(desc(m))

data_median = data %>% 
  group_by(group, comb) %>% 
  summarize(wpd_med = median(wpd))

data_pcp <- data_median %>% 
mutate(group = as.character(group)) %>% 
  left_join(data_order) %>% 
  arrange(desc(m)) %>% 
  pivot_wider(-4, 
              names_from = comb, 
              values_from = wpd_med)

parcoord <- GGally::ggparcoord(data_pcp,
                   columns = 2:ncol(data_pcp),
                   groupColumn = 1,
                   showPoints = TRUE, 
                   title = "(c)",
                   alphaLines = 0.8,
                   scale = "globalminmax"
) + ggplot2::theme_bw() +
  scale_color_viridis(discrete=TRUE) + 
  ggplot2::theme(
    plot.title = ggplot2::element_text(size=10)
  )+
  ggplot2::theme(axis.text.y = ggplot2::element_text(angle = 0)) +
  theme(legend.position = "bottom") +
  xlab("") +
  ylab("wpd")

##----read-orig-data

@@

sm_hod_dow <- elec %>% 
gravitas::create_gran("hour_day") %>% 
  gravitas::create_gran("day_week")

@@

  sm_hod_dow %>% 
  filter(group==1) %>% 
  gravitas::prob_plot(
     "day_week",
     "hour_day",
  response = "kwh",
  plot_type = "quantile", nrow=1) +
  scale_y_log10() +
    ggtitle("Group 1")

  sm_hod_dow %>% 
  filter(group==2) %>% 
  gravitas::prob_plot(  "day_week",
     "hour_day",
  response = "kwh",
  plot_type = "quantile", nrow=1) +
  scale_y_log10()+
    ggtitle("Group 2")

  sm_hod_dow %>% 
  filter(group==3) %>% 
  gravitas::prob_plot(  "day_week",
     "hour_day",
  response = "kwh",
  plot_type = "quantile", nrow=1) +
  scale_y_log10() +
    ggtitle("Group 3")

  sm_hod_dow %>% 
  filter(group==4) %>% 
  gravitas::prob_plot("day_week",
     "hour_day",
  response = "kwh",
  plot_type = "quantile", nrow=1) +
  scale_y_log10() +
    ggtitle("Group 4")
```
<!-- ncol_sm <- seq_len(ncol(sm_hod_list))[-ncol(sm_hod_list)] -->
<!-- nrow_sm <- seq_len(nrow(sm_hod_list)) -->

@@

>>>>

---
title: "Algorithm using wpd values for clustering 8 households"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,echo=FALSE, message=FALSE, warning = FALSE)
```

@@

hc = stats::hclust(dist(data_clust[-1], method="manhattan"),method="complete")
#plot(hc)

library(fpc)
koptimal = fpc::nselectboot(dist(data_clust[-1], method="manhattan"),
                        B = 50,
                        method = "complete",
                        clustermethod = disthclustCBI, 
                        classification = "averagedist",
                        krange = 2:5)

koptimal = koptimal$kopt
koptimal

@@

groups %>% 
  dplyr::group_by(value) %>%  
  summarise(n = n())

data_wide <- data_clust %>% left_join(groups) %>%
  rename("group" = "value") %>% 
  mutate(group = as.factor(group)) %>% ungroup()

@@

parcoord <- GGally::ggparcoord(data_wide,
                   columns = 2:(ncol(data_wide)-1),
                   groupColumn = "group",
                   showPoints = TRUE, 
                   title = "(c)",
                   alphaLines = 0.8,
                   scale = "globalminmax"
) + ggplot2::theme_bw() +
  scale_color_brewer(palette = "Dark2") + 
  ggplot2::theme(
    plot.title = ggplot2::element_text(size=10)
  )+
  ggplot2::theme(axis.text.y = ggplot2::element_text(angle = 0)) +
  theme(legend.position = "bottom") +
  xlab("") +
  ylab("wpd")

# data = data_clust %>% 
# left_join(groups)%>% 
#              rename ("group" = "value") %>% 
#              ungroup() %>% 
#              select(group, everything(), -id) %>% 
#              pivot_longer(-1, names_to = "comb", values_to = "wpd")
# 
# data_order <- data %>% 
#   group_by(comb) %>% 
#   summarise(m = mean(wpd)) %>% 
#   arrange(desc(m))
#   
# data_median = data %>% 
#   group_by(group, comb) %>% 
#   summarize(wpd_med = median(wpd))
# 
# data_pcp <- data_median %>% 
# mutate(group = as.character(group)) %>% 
#   left_join(data_order) %>% 
#   arrange(desc(m)) %>% 
#   pivot_wider(-4, 
#               names_from = comb, 
#               values_from = wpd_med) 
#              
# parcoord <- GGally::ggparcoord(data_pcp,
#                    columns = 2:ncol(data_pcp),
#                    groupColumn = 1,
#                    showPoints = TRUE, 
#                    title = "(c)",
#                    alphaLines = 0.8,
#                    scale = "globalminmax"
# ) + ggplot2::theme_bw() +
#   scale_color_viridis(discrete=TRUE) + 
#   ggplot2::theme(
#     plot.title = ggplot2::element_text(size=10)
#   )+
#   ggplot2::theme(axis.text.y = ggplot2::element_text(angle = 0)) +
#   theme(legend.position = "bottom") +
#   xlab("") +
#   ylab("wpd")
```

```{r}
##----read-orig-data

@@

ggpairs_nocolor <- ggpairs(data_wide, columns = 2:(ncol(data_wide)-1))
ggpairs_nocolor

sm_hod_dow <- elec %>% 
gravitas::create_gran("hour_day") %>% 
  gravitas::create_gran("day_week") %>% 
    dplyr::mutate(kwh = scale(kwh))

@@

  sm_hod_dow %>% 
  filter(group==1) %>% 
  gravitas::prob_plot(
     "day_week",
     "hour_day",
  response = "kwh",
  plot_type = "quantile", nrow=1) +
  #scale_y_log10() +
    ggtitle("Group 1")

  sm_hod_dow %>% 
  filter(group==2) %>% 
  gravitas::prob_plot(  "day_week",
     "hour_day",
  response = "kwh",
  plot_type = "quantile", nrow=1) +
  #scale_y_log10()+
    ggtitle("Group 2")

  sm_hod_dow %>% 
  filter(group==3) %>% 
  gravitas::prob_plot(  "day_week",
     "hour_day",
  response = "kwh",
  plot_type = "quantile", nrow=1) +
  #scale_y_log10() +
    ggtitle("Group 3")

  sm_hod_dow %>% 
  filter(group==4) %>% 
  gravitas::prob_plot("day_week",
     "hour_day",
  response = "kwh",
  plot_type = "quantile", nrow=1) +
  #scale_y_log10() +
    ggtitle("Group 4")
```
<!-- ncol_sm <- seq_len(ncol(sm_hod_list))[-ncol(sm_hod_list)] -->
<!-- nrow_sm <- seq_len(nrow(sm_hod_list)) -->

@@

```

### 2021-08-18 supplementary/algorithm2/real-data/handpick_distinct_cust.Rmd
cleaning folders

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```

@@

group_data_orig %>% 
  ungroup() %>% 
  rename("pred" = "pred_design", "cust" = "customer_id") %>% 
  #filter(group==3) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
  ggplot(aes(x = as.integer(day_month), y = median_kwh)) +
  geom_line(size = 0.5) +
  facet_wrap(pred~cust,
             labeller = "label_context",
             scales = "free_y") + 
  theme_minimal()+ theme(strip.text.y = element_text(size = 5)) + scale_y_log10() + scale_x_continuous(breaks=seq(1, 31, 7), minor_breaks = seq(1, 31, 7))+ 
       theme(strip.text.x = element_text(size = 6, margin = margin(b = 0, t = 0)))+ xlab("dom")
# 
group_data_orig$customer_id <-factor(group_data_orig$customer_id, levels = elec_pred_wo_scaled$customer_id)

>>>>

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  #geom_line(aes(y = `50%`), size = 0.7) +
  geom_smooth(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```

@@

group_data_orig %>% 
  ungroup() %>% 
  rename("pred" = "pred_design", "cust" = "customer_id") %>% 
  #filter(group==3) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
  ggplot(aes(x = as.integer(day_month), y = median_kwh)) +
  geom_line(size = 0.5) +
  facet_wrap(pred~cust,
             labeller = "label_context",
             scales = "free_y") + 
  theme_minimal()+ theme(strip.text.y = element_text(size = 5)) + scale_y_log10() + scale_x_continuous(breaks=seq(1, 31, 7), minor_breaks = seq(1, 31, 7))+ 
       theme(strip.text.x = element_text(size = 6, margin = margin(b = 0, t = 0)))+ xlab("dom")

### new quantile scale
quantile_prob_val = c(0.25, 0.5, 0.75)

sm_hod <- gravitas::create_gran(data_pick, "day_month")

sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(design, customer_id, day_month, general_supply_kwh) %>% 
  pivot_wider(names_from = day_month,
              values_from = general_supply_kwh)

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  #geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") +
  geom_smooth(aes(y = `50%`)) +
   geom_smooth(aes(y = `25%`), se = FALSE) +
   geom_smooth(aes(y = `75%`), se = FALSE) +
  scale_y_log10()

### all same scale 
group_data_orig$customer_id <-factor(group_data_orig$customer_id, levels = elec_pred_wo_scaled$customer_id)
